Cryptographic assurance of secrecy and fairness in voting

### 2012-12-06 paper/paper.tex
Make all first-person clauses present tense.

In this survey, we will study three of the most well-known solutions: the in-person voting systems
Scantegrity and \pv{} and the online voting system Helios.

First, we will discuss the background of verifiable voting schemes and the security goals they
strive to satisfy. Second, we will describe each of the three voting schemes in turn. We will then
analyze their differing approaches to security and how well they achieve the desired goals. Finally,
we will present some ideas that are not -- but perhaps should be -- considered by these schemes, and
we will draw conclusions about the role of these schemes in elections today and in the future.

@@

Though ballot secrecy prevents such a party from determining that a voter has done as asked, it is a
different problem to ensure that even the voter herself cannot prove that her ballot was
cast a certain way. We will show, in describing these systems, that the cryptographic techniques
used to provide ballot secrecy also ensure -- in the case of in-person elections -- that a voter
cannot prove her ballot was cast a certain way even with the data necessarily exposed to provide
verifiability.

@@

This process will be discussed further in the analysis.

@@

We will analyze these voting systems by considering each security goal in turn.

>>>>

In this survey, we study three of the most well-known solutions: the in-person voting systems
Scantegrity and \pv{} and the online voting system Helios.

First, we discuss the background of verifiable voting schemes and the security goals they
strive to satisfy. Second, we describe each of the three voting schemes in turn. We then
analyze their differing approaches to security and how well they achieve the desired goals. Finally,
we present some ideas that are not -- but perhaps should be -- considered by these schemes, and
we draw conclusions about the role of these schemes in elections today and in the future.

@@

Though ballot secrecy prevents such a party from determining that a voter has done as asked, it is a
different problem to ensure that even the voter herself cannot prove that her ballot was
cast a certain way. We show, in describing these systems, that the cryptographic techniques
used to provide ballot secrecy also ensure -- in the case of in-person elections -- that a voter
cannot prove her ballot was cast a certain way even with the data necessarily exposed to provide
verifiability.

@@

We further discuss this process in our analysis.

@@

We analyze these voting systems by considering each security goal in turn.
